%-------------------------
% Resume in Latex
% Author: Jay Bhensdadia
%------------------------

\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jay Bhensdadia}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:jayvpatel29@gmail.com}{jayvpatel29@gmail.com} | \href{tel:+919925565112}{+919925565112}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{IBM}
\descript{| Backend Developer }
\location{Oct 2024 – Present | Bangalore, India}
\vspace{\topsep}
\begin{tightemize}
% High-level, big impact bullets first
\item Contributing to IBM Cloud Networking (IaaS), collaborating across Private DNS, LBaaS, and Developer Experience teams (UI, CLI, Terraform, SDK).
\item Co-designed and implemented key components of \textbf{Phoenix}, a recovery microservice for LBaaS that enables immediate recovery of stuck load balancers, reducing reliance on manual processes and periodic Jenkins jobs.

% Technical depth bullets next
\item Worked on Private DNS control path migration from ETCD to Redis, implementing a polling-based mechanism to replace ETCD’s native watch events for reliable state monitoring.
\item Developed LuaScripts to identify expired VSI leases, enabling reliable polling in place of ETCD watch events.
\item Integrated admin APIs into the operations dashboard, simplifying token management and API queries, and significantly reducing manual SRE effort.
\item Maintained and extended client tools (\textbf{UI: React + Express}, \textbf{CLI: Go}, \textbf{Terraform provider: Go}, \textbf{SDKs: Java, Python, Go, JavaScript}), supporting networking service feature releases across teams.
\end{tightemize}
\sectionsep

\runsubsection{Silvertouch Technologies}
\descript{| Software Development Engineer | (Intern + Full Time)}
\location{Jan 2024 – Oct 2024 | Ahmedabad, India}
\begin{tightemize}
% Highlight high-impact bullets first
\item Completed 6-month internship training across Spring Boot, React, Angular, iOS (Swift), and Flutter, developing adaptability and rapid learning skills to contribute quickly to projects.
\item Single handedly designed and implemented asynchronous, atomic integration between HRMS (Java) and Odoo Accounting module, ensuring accurate event-based accounting entries (claims, loans, salaries) without duplicates.


% Technical depth bullets
\item Optimized HRMS admin dashboards by consolidating multiple queries into database views, reducing page load time from 10–15 seconds to under 1 second.
\item Co-developed production database sanitization script for a 1200+ table HRMS schema, leveraging ON-DELETE CASCADE to safely remove dummy users and related data without affecting real users.
\end{tightemize}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Munimji}
\descript{| Expense Tracker for Developers}
\location{Spring Boot | Keycloak | Postgres | Docker | Next.js | Redis | Kubernetes}
\begin{tightemize}
\item Developed a full-stack expense tracker with CRUD, category management, and automated cloud bill fetching (AWS, Azure) via IAM role integration.
\item Built a minimal \textbf{Next.js} dashboard with \textbf{Spring Boot} backend, \textbf{Postgres} DB, and \textbf{Redis}-based session storage for distributed pods.
\item Integrated \textbf{Keycloak} for authentication and containerized services with \textbf{Docker} for scalable deployment on \textbf{Kubernetes}.
\item \href{https://github.com/JayBhensdadia/munimjii}{Repository Link}
\end{tightemize}
\sectionsep





% \runsubsection{Chit Chat}
% \descript{| Class Project for Distributed Client-Server Programming}
% \location{Jan 2018 – May 2018 | Somewhere, XX}
% \begin{tightemize}
% \item Lead the development of \textbf{\href{https://github.com/user/repo}{Chit Chat}}, an anonymous chat application created as a class project.
% \item Chit Chat provides real-time communication while utilizing a PHP backend and AngularJS frontend.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{Cornell Robot Learning Lab}
% \descript{| Researcher}
% \location{Jan 2014 – Jan 2015 | Ithaca, NY}
% Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.
% \sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COMMUNITY SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Community Service}

% \begin{tabular}{rll}
% 2013 -- 2018    & Tennessee     & St. Baldrick's Foundation\\
% 2014 -- 2017	& Tennessee     & American Cancer Society's Hope Lodge\\
% 2013 -- 2015    & Tennessee     & Habitat for Humanity\\
% 2011 -- 2015    & Tennessee     & Special Olympics\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies}

% \begin{tabular}{rll}
% 2018 -- 2018    & National      & Association of Computing Machinery (ACM)\\
% 2017 -- 2019	& National      & Scrum Alliance Certified ScrumMaster\\
% 2015 -- 2019    & University    & Shackouls Honors College\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards}
% \begin{tabular}{rll}
% 2015        & 99\textsuperscript{th} percentile & National Merit Scholarship Finalist\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications}
% \renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Vishwakarma Government Engineering College}
\descript{Bachelor of Engineering in Computer Science}
\location{2024 | Ahmedabad, India}
% College of Engineering \\
% Dean's List (All Semesters) \\
\location{ CGPA: 9.33 / 10.0}
\sectionsep

\subsection{Shri Hari International Public School}
\descript{Class XII}
\location{2020 | Gandhinagar, India}
% College of Engineering \\
% Dean's List (All Semesters) \\
\location{ Percentage: 85\%}
\sectionsep

\subsection{Mount Carmel High School}
\descript{Class X}
\location{2018 | Gandhinagar, India}
% College of Engineering \\
% Dean's List (All Semesters) \\
\location{ Percentage: 95\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
% \location{3+ years:}
Java \textbullet{} Go \\
% \location{1+ years:}
TypeScript \textbullet{} JavaScript \\
\sectionsep

\subsection{Technology}
Git/Github \textbullet{} Cloud \textbullet{} Docker \\
Kuberenetes \textbullet{} Spring Boot \textbullet{} Microservices \\
Cloud Native \textbullet{} MERN \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRACURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurricular}
\subsection{Open Source Contribution}
Contributed to \textbf{Refine.dev}, a React-based open-source framework. \\
\href{https://github.com/refinedev/refine/pull/6021}{Pull Request Link}
\sectionsep

\subsection{Bootcamp}
Completed \textbf{IBM SkillsBuild Data Analytics Innovation Camp 2022}, focused on data analysis, visualization, and cloud-based problem solving.
\sectionsep

\subsection{Online Internship}
Tatvasoft Summer Internship — Developed a full-stack \textbf{bookstore platform} enabling buyers and sellers to transact books. \\
\href{https://github.com/JayBhensdadia/Tatvasoft}{Project Repository}
\sectionsep


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     Societies
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies}
% Association for Computing Machinery (ACM)\\
% Scrum Alliance Certified ScrumMaster\\
% University Honors College\\
% National Merit Scholarship Finalist \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/jaybhensdadia/}{\bf JayBhensdadia} \\
LinkedIn://  \href{https://www.linkedin.com/in/jay-bhensdadia/}{\bf jay-bhensdadia}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}